---
title: "Penguin Assignment"
output: html_document
---
# Load functions:
```{r}
source("functions/libraries.r")
source("functions/cleaning.r")
source("functions/plotting.r")
```
# Load the data:
```{r}
penguins_raw <- read.csv("data_raw/penguins_raw.csv")
```
# Clean the data: fix column names
```{r}
penguins_clean <- cleaning(penguins_raw)
```
# Save the cleaned data:
```{r}
write.csv(penguins_clean, "data_clean/penguins_clean.csv")
```

# Subset the data to exclude everything except species, flipper length and body mass. Any rows with missing data will also be removed: 
```{r}
penguins_flippers_body <- remove_empty_flipper_body(penguins_clean)
```
# Linear regression model between body mass and flipper length
```{r}
body_mass_flipper_length_lm <- lm(flipper_length_mm ~ body_mass_g, penguins_flippers_body)
summary(body_mass_flipper_length_lm)
confint(body_mass_flipper_length_lm)
```
# ANOVA for the linear regression:
```{r}
anova(body_mass_flipper_length_lm)
```
## The P value is less than 0.05, suggesting that there is a significant correlation between body mass and flipper length, and so flipper length can be predicted from body mass. 

# Plot a scatter graph showing the relationship between body mass (g) and flipper length (mm):
```{r}
body_mass_flipper_length_scattergraph <- plot_body_mass_flipper_length_figure(penguins_flippers_body)
```
# Generate the scatter graph showing the relationship between body mass (g) and flipper length (mm):
```{r}
body_mass_flipper_length_scattergraph
```
# Save the figure as a png, svg and pdf:
```{r}
agg_png("figures/same_size.png", 
        width = 500, height = 500, units = "px")
body_mass_flipper_length_scattergraph
dev.off()

ggsave(file="figures/test.svg", plot=body_mass_flipper_length_scattergraph, width=10, height=8)

ggsave(file="figures/test.pdf", plot=body_mass_flipper_length_scattergraph, width=10, height=8)
```

